Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-07-07 tex/ms.tex
outline required figures and tables

Imagine you have three photometric bands through which you have
observed some object (independently, say), and also a 2500-pixel
spectrum, where the pixels are defined such that they are precisely or
approximately independent measurements.
For these purposes, two spectral pixels are very close to independent
measurements if they are derived from disjoint sets of detector pixels
in the spectrograph detector plane.
Each photometric band and each spectroscopic pixel has a
log-likelihood function, and these 2503 log-likelihood functions must
be (by the Rules of Righteousness) coadded equally into one full-data
log-likelihood.
The log-likelihood is therefore fully dominated by the spectral
pixels!
This despite the fact that in almost all astronomical investigations,
the photometry is far more reliable, per measurement, than the
spectra.
That is, if the spectral pixels tend to prefer one model, or one set
of parameters, and the photometry another, the spectra will almost
always ``win'' just by their overwhelming force.

@@

We are now left to demonstrate that it is possible to infer the
parameters of interest $\theta$ while marginalizing over the
calibration parameters $\alpha$.  We will apply the methodology for
spectrophotometric calibration described above to an \emph{actual,
real} optical spectrum of a stellar cluster in M31.  Spectra of star
clusters provide a good test case, as they are less complex than
galaxy spectra (for which it is necessary to model the star formation
history) but are by no means trivial. In this way the key features of
the calibration model and methodology are not obscured.

To demonstrate the effectiveness of our spectrophotometric calibration
strategy we will infer the parameters $\theta$ from a spectrum both
\emph{before} and \emph{after} it has been spectrophotometrically
calibrated using typical techniques and ancillary spectrophotometric
calibration data.

@@

The data we use to test our method consists of optical spectroscopy of
XX stellar clusters in M31 for which YY-band HST photometric data
exist.  The optical spectra were obtained using the fiber-fed
Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
of the spectra is $3700-7200 \AA$. The instrumental resolution is
$\sim 5\AA$ across the optical range \citep{fabricant13}.  Wavelength
calibration happened. Sky subtraction happened. The data were
approximately spectrophotometrically calibrated using an average
calibration vector for the night constructed from.... (MORE HERE). Figure
\ref{fig:data} shows the spectra before and after calibration for each
cluster.  Discuss S/N, sky subtraction.

@@

@@

We first infer the parameters of interest $\theta$ for a calibrated
spectrum of one of the clusters, using the full YY-band photometry. In
Figure \ref{fig:calibrated_spectrum} we show the spectrum resulting
from draws of the parameters $[\theta,\alpha]$ from the posterior
distribution.  This figure also shows the calibrated spectrum on which
the priors were conditioned, and several of the individual components
of the model constructed from each draw.  In Figure
\ref{fig:calibrated_residuals} we show the residuals between the data
and the draws from the posterior, for both the spectra and the
photometry. In Figure \ref{fig:calibrated_triangle} we show the
marginalized and joint PDFs for the parameters.

@@

BDJ: Then, we show select marginalized or joint PDFs for each cluster
calibrated/uncalibrated, to assess consistency.

@@

>>>>

Imagine you have three photometric bands through which you have
observed some object (independently, say), and also a 2500-pixel
spectrum, where the pixels are defined such that they are precisely or
approximately independent measurements.
For these purposes, two spectral pixels are very close to independent
measurements if they are derived from disjoint sets of detector pixels
in the spectrograph detector plane.
Each photometric band and each spectroscopic pixel has a
log-likelihood function, and these 2503 log-likelihood functions must
be (by the Rules of Righteousness) coadded equally into one full-data
log-likelihood.
The log-likelihood is therefore fully dominated by the spectral
pixels!
This despite the fact that in almost all astronomical investigations,
the photometry is far more reliable, per measurement, than the
spectra.
That is, if the spectral pixels tend to prefer one model, or one set
of parameters, and the photometry another, the spectra will almost
always ``win'' just by their overwhelming numbers.

@@

We are now left to demonstrate that it is possible to infer the
parameters of interest $\theta$ while marginalizing over the
calibration parameters $\alpha$.  We will apply the methodology for
spectrophotometric calibration described above to \emph{actual,
real} optical spectra of a stellar clusters in M31.  Spectra of star
clusters provide a good test case, as they are less complex than
galaxy spectra (for which it is necessary to model the star formation
history) but are by no means trivial. In this way the key features of
the calibration model and methodology are not obscured.

To demonstrate the effectiveness of our strategy for combining
spectroscopic and photometric information we will infer the parameters
$\theta$ from a spectrum both \emph{before} and \emph{after} it has
been spectrophotometrically calibrated using typical techniques and
ancillary spectrophotometric calibration data.

@@

The data we use to test our method consists of optical spectroscopy of
XX stellar clusters in M31 for which YY-band HST photometric data
exist.  The optical spectra were obtained using the fiber-fed
Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
of the spectra is $3700-7200 \AA$. The instrumental resolution is
$\sim 5\AA$ across the optical range \citep{fabricant13}.  Wavelength
calibration happened. Sky subtraction happened. The data were
approximately spectrophotometrically calibrated using an average
calibration vector for the night constructed from.... (MORE
HERE). Figure \ref{fig:data} shows the spectra before and after
calibration (SHOULD THIS SHOW ALL THE CLUSTERS OR JUST ONE?).  Discuss
S/N, sky subtraction.

\begin{figure}[h!]
\caption{Shows the calibrated and uncalibrated spectrum for one
  cluster, along with the uncertainty spectrum and (maybe) the
  calibration vector. \label{fig:data}}
\end{figure}

\begin{table}[h!]
\caption{List all the clusters, and individual exposures.}
\end{table}

@@

\begin{table}[h!]
\caption{List the parameters and  their allowed ranges.}
\end{table}

@@

We first infer the parameters of interest $\theta$ for a calibrated
spectrum of one of the clusters, using the full YY-band photometry. In
Figure \ref{fig:calibrated_spectrum} we show the spectrum resulting
from draws of the parameters $[\theta,\alpha]$ from the posterior
distribution.  This figure also shows the calibrated spectrum on which
the priors were conditioned, and several of the individual components
of the model constructed from each draw.  In Figure
\ref{fig:calibrated_spectrum} we also show the residuals between the data
and the draws from the posterior, for both the spectra and the
photometry. In Figure \ref{fig:calibrated_triangle} we show the
marginalized and joint PDFs for the parameters.

@@

BDJ: Then, we show select marginalized or joint PDFs for each cluster
calibrated/uncalibrated, to assess consistency.  They are very consistent.

@@

\begin{figure}[h!]
\caption{Show, for one cluster, the (un)calibrated spectral data, draws from
  the posterior for the model, and residuals}
\end{figure}

\begin{figure}[h!]
\caption{Show the observed photometric SED and draws from the
  posterior, for one cluster.}
\end{figure}

\begin{figure}[h!]
\caption{Show a corner plot of selected relevant parameters, for one cluster.}
\end{figure}

\begin{figure}[h!]
\caption{Money plot.  Show the difference between the parameters
  inferred from the calibrated and uncalibrated spectra, for each cluster.}
\end{figure}
